Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
chore: more in the evaluation

\section{Evaluation}
\label{sec:eval}
\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{imgs/example.png}
  \label{fig:example}
  \caption{Simulation of the case study scenario in Alchemist. 
  The dots represent the robots, 
  the circle area on the top right represents the phenomenon to be monitored, 
  and the grey area represents the area covered by the robots.}
\end{figure}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal. The individual agents do not have any knowledge of the initial phenomenon itself (i.e., shape, size, location, velocity,...).
 %
 Initially, 
  we perform the training phase using a stationary phenomenon before expanding towards a moving phenomenon in the test phase. 
  %Additionally, the phenomenon can change its shape during runtime. 
  Finally, the phenomenon may have varying areas of interest, defined by an underlying distribution function. '

\subsection{Scenario}
Figure~\ref{fig:example} illustrates the scenario used during the learning, 
which consists of a set of 25 agents and a single, stationary phenomenon with a 3D Gaussian 
Each agent can perceive the presence
 of the phenomenon of interest through an installed sensor $\zeta_v$ with $v \in \mathbb{V}$. 
 (e.g., camera, temperature sensor, etc.). 
%
Additionally, each agent has a coverage range $\omega$ (fixed to 7.5 meters) 
 that describes the area it can monitor. 
 Each agent can only communicate directly with its own neighbourhood $\mathcal{N}$, 
 which in this case depends on a $\mathbb{O}$ range fixed to 30 meters. \lukas{$\mathbb{O}$  not defined.}
From the neighbourhood, 
 each agent can also perceive the direction of the other agents.
%
Each agent moves following a certain action composed of two components ($\alpha$, $\theta$) 
 which respectively describe the angle and intensity of the movement (i.e., the velocity vector).
 \lukas{drone, robot, agent, node...}
\subsection{Goal}
 The objective of this scenario is threefold:
\begin{enumerate}
\item Maximise the number of agents within the phenomena
\item Minimise the number of agents without a neighbourhood
\item Maximise the coverage of the system
\end{enumerate}

>>>>

\section{Evaluation}
\label{sec:eval}
\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{imgs/example.png}

  \caption{Simulation of the case study scenario in Alchemist. 
  The dots represent the robots, 
  the circle area on the top right represents the phenomenon to be monitored, 
  and the grey area represents the area covered by the robots.}
  \label{fig:example}
\end{figure}
\ga{Page budget: 2 pages \\}
%\ga{Plan: we should discuss the robot aggregation scenario, specifying the state space, the action space, and the reward function.
%I dunno if it makes sense to discuss the variants (i.e., fixed area, two areas and moving area). We will see.}
To test the effectiveness of the proposed approach, 
 we decided to experiment with a case study related to swarm robotics, 
 specifically the tracking and coverage of a spatio-temporal phenomenon, cf. tracking a wildfire 
 or monitoring the water levels in a canal. The individual agents do not have any knowledge of the initial phenomenon itself (i.e., shape, size, location, velocity,...).
 %
Initially, 
  we perform the training phase using a stationary phenomenon before expanding towards a moving phenomenon in the test phase. 
  %Additionally, the phenomenon can change its shape during runtime. 
  Finally, the phenomenon may have varying areas of interest, defined by an underlying distribution function.
As a simulation environment, we use Alchemist~\cite{alchemist}, 
 a simulator for multi-agent systems that allows us to simulate the swarm behaviour of the agents 
 and the phenomenon of interest.
For the \ac{GNN}, we use the implementation provided by PyTorch Geometric~\cite{Fey/Lenssen/2019}, 
 which is a library for deep learning on graphs built on top of PyTorch~\cite{torch}.
Finally, we use ScaFi~\cite{casadei2022scafi} as the aggregate programming language to support 
 our field-informed approach.

\subsection{Scenario}
Figure~\ref{fig:example} illustrates the scenario used during the learning, 
which consists of a set of 25 agents and a single, stationary phenomenon with a 3D Gaussian 
Each agent can perceive the presence
 of the phenomenon of interest through an installed sensor $\zeta_v$ with $v \in \mathbb{V}$. 
 (e.g., camera, temperature sensor, etc.). 
%
Additionally, each agent has a coverage range $\omega$ (fixed to 7.5 meters) 
 that describes the area it can monitor. 
 Each agent can only communicate directly with its own neighbourhood $\mathcal{N}$, 
 which in this case depends on a $\mathbb{O}$ range fixed to 30 meters. %\lukas{$\mathbb{O}$  not defined.}
From the neighbourhood, 
 each agent can also perceive the direction of the other agents.
%
Each agent moves following a certain action composed of two components ($\alpha$, $\theta$) 
 which respectively describe the angle and intensity of the movement (i.e., the velocity vector).
 %\lukas{drone, robot, agent, node...}
\subsection{Goal}
 The objective of this scenario is threefold:
\begin{enumerate}
\item Maximise the number of agents within the phenomena
\item Minimise the number of agents without a neighbourhood
\item Maximise the coverage of the system
\end{enumerate}
